---
title: "Lexical Diversity in Speakers of Spanish as a Heritage Language"
author: "Christopher Stewart"
date: "May 14, 2015"
output: html_document
---

# Introduction 

This project examines lexical diversity in oral interviews with three groups of heritage Spanish speakers: highly proficient speakers, speakers with more limited fluency and speakers who rarely use Spanish.

## Data preparation and exploration

### Data Acquisition
These data were sent to me in an email by Maria Ciriza. I received Word files that I converted into text files, first excising elements that are obviously extraneous to the analysis to be performed (i.e. headings, numbers, etc.), then compressing them and placing them in a [GitHub repository](https://github.com/cmstewart/spanish_hl). 

In addition to the data files, this script can be found in the same repository, in the interest of making sure that this analysis is fully reproducible.

To begin, download the text files from the repository and switch working directories to the folder where the files where downloaded. We initially print out the working directory used here and its contents to show what your working directory should look like.

```{r data acquisition}
# Set working directory and print out its contents
getwd()
list.files()

```

## Data cleaning

To begin with, we clean our corpus to prepare it for model building. This code chunk is for illustrative purposes *only*, so that you can see what the code looks like. Future code blocks will be hidden from view in the HTML document produced.

```{r cleanup data}
# Load required packages
suppressPackageStartupMessages(require("stringr"))

# load in data from 3 groups
group1_corp <- readLines("group1.txt")
group2_corp <- readLines("group2.txt")
group3_corp <- readLines("group3.txt")

# convert all text to lower case
group1_corp.1 <- tolower(group1_corp)
group2_corp.1 <- tolower(group2_corp)
group3_corp.1 <- tolower(group3_corp)

# replace punctuation with single space
group1_corp.2 <- str_replace_all(group1_corp.1, "[^[:alnum:]]", " ")
group2_corp.2 <- str_replace_all(group2_corp.1, "[^[:alnum:]]", " ")
group3_corp.2 <- str_replace_all(group3_corp.1, "[^[:alnum:]]", " ")

# eliminate digits, replace heading and trailing spaces left behind by corpus cleanup
group1_corp.3 <- str_replace_all(group1_corp.2, "[[:digit:]]+", " ")
group1_corp.c <- str_replace_all(group1_corp.3, "  ", replacement = " ")

group2_corp.3 <- str_replace_all(group2_corp.2, "[[:digit:]]+", " ")
group2_corp.c <- str_replace_all(group2_corp.3, "  ", replacement = " ")

group3_corp.3 <- str_replace_all(group3_corp.2, "[[:digit:]]+", " ")
group3_corp.c <- str_replace_all(group3_corp.3, "  ", replacement = " ")

# Clean up
rm(group1_corp); rm(group2_corp); rm(group3_corp)
rm(group1_corp.1); rm(group2_corp.1); rm(group3_corp.1)
rm(group1_corp.2); rm(group2_corp.2); rm(group3_corp.2)
rm(group1_corp.3); rm(group2_corp.3); rm(group3_corp.3)

```

### Tokenization, n-gram constructions, frequency tables and n-gram probabilities

We now tokenize and produce 2-, 3- and 4-grams using Maciej Szymkiewicz's efficient [Ngrams_tokenizer](https://github.com/zero323/r-snippets/blob/master/R/ngram_tokenizer.R) function.

```{r tokenize, echo=FALSE}

# load tokenizer function, then make function for bigram, trigram and tetragram construction
source("Ngrams_tokenizer.R")
tokenizer <- ngram_tokenizer(1)
bigram.tokenizer <- ngram_tokenizer(2)
trigram.tokenizer <- ngram_tokenizer(3)
tetragram.tokenizer <- ngram_tokenizer(4)
pentagram.tokenizer <- ngram_tokenizer(5)

# tokenize corpora from 3 groups
group1_corp_c_tok <- tokenizer(group1_corp.c)
group2_corp_c_tok <- tokenizer(group2_corp.c)
group3_corp_c_tok <- tokenizer(group3_corp.c)

# Clean up
rm(group1_corp.c); rm(group2_corp.c); rm(group3_corp.c)

# build bigrams
group1_corp_c_bi <- bigram.tokenizer(group1_corp_c_tok)
group2_corp_c_bi <- bigram.tokenizer(group2_corp_c_tok)
group3_corp_c_bi <- bigram.tokenizer(group1_corp_c_tok)

# build trigrams
group1_corp_c_tri <- trigram.tokenizer(group1_corp_c_tok)
group2_corp_c_tri <- trigram.tokenizer(group2_corp_c_tok)
group3_corp_c_tri <- trigram.tokenizer(group3_corp_c_tok)

# build tetragrams
group1_corp_c_tetra <- tetragram.tokenizer(group1_corp_c_tok)
group2_corp_c_tetra <- tetragram.tokenizer(group2_corp_c_tok)
group3_corp_c_tetra <- tetragram.tokenizer(group3_corp_c_tok)

# build pentagrams
group1_corp_c_pent <- pentagram.tokenizer(group1_corp_c_tok)
group2_corp_c_pent <- pentagram.tokenizer(group2_corp_c_tok)
group3_corp_c_pent <- pentagram.tokenizer(group3_corp_c_tok)

```

Next, we use R's ["data table"](http://cran.r-project.org/web/packages/data.table/index.html) package to store and organize our n-grams.

```{r organize n-grams, echo=FALSE}
# load required packages
suppressPackageStartupMessages(require("data.table"))

# FOR TOKENS: switch to "data tables", set appropriate column names
group1_corp_c_tokDT <- as.data.table(group1_corp_c_tok); setnames(group1_corp_c_tokDT, "tokens")
group2_corp_c_tokDT <- as.data.table(group2_corp_c_tok); setnames(group2_corp_c_tokDT, "tokens")
group3_corp_c_tokDT <- as.data.table(group3_corp_c_tok); setnames(group3_corp_c_tokDT, "tokens")

# FOR BIGRAMS: switch to "data tables", set appropriate column names
group1_corp_c_biDT <- as.data.table(group1_corp_c_bi); setnames(group1_corp_c_biDT, "bigrams")
group2_corp_c_biDT <- as.data.table(group2_corp_c_bi); setnames(group2_corp_c_biDT, "bigrams")
group3_corp_c_biDT <- as.data.table(group3_corp_c_bi); setnames(group3_corp_c_biDT, "bigrams")

# FOR TRIGRAMS: switch to "data tables", set appropriate column names
group1_corp_c_triDT <- as.data.table(group1_corp_c_tri); setnames(group1_corp_c_triDT, "trigrams")
group2_corp_c_triDT <- as.data.table(group2_corp_c_tri); setnames(group2_corp_c_triDT, "trigrams")
group3_corp_c_triDT <- as.data.table(group3_corp_c_tri); setnames(group3_corp_c_triDT, "trigrams")

# FOR TETRAGRAMS: switch to "data tables", set appropriate column names
group1_corp_c_tetraDT <- as.data.table(group1_corp_c_tetra); setnames(group1_corp_c_tetraDT, "tetragrams")
group2_corp_c_tetraDT <- as.data.table(group2_corp_c_tetra); setnames(group2_corp_c_tetraDT, "tetragrams")
group3_corp_c_tetraDT <- as.data.table(group3_corp_c_tetra); setnames(group3_corp_c_tetraDT, "tetragrams")

# FOR PENTAGRAMS: switch to "data tables", set appropriate column names
group1_corp_c_pentDT <- as.data.table(group1_corp_c_pent); setnames(group1_corp_c_pentDT, "pentagrams")
group2_corp_c_pentDT <- as.data.table(group2_corp_c_pent); setnames(group2_corp_c_pentDT, "pentagrams")
group3_corp_c_pentDT <- as.data.table(group3_corp_c_pent); setnames(group3_corp_c_pentDT, "pentagrams")

```

We use these new data tables to now derive frequency counts for our n-grams.

```{r get frequency counts, echo=FALSE}

# Get frequency counts, eliminate repeated n-grams (we only need the count for each once) and order by descending n-gram frequency

## TOKENS
group1_corp_c_tokDTfreqs <- group1_corp_c_tokDT[,token.count:=.N, by = tokens]
group2_corp_c_tokDTfreqs <- group2_corp_c_tokDT[,token.count:=.N, by = tokens]
group3_corp_c_tokDTfreqs <- group3_corp_c_tokDT[,token.count:=.N, by = tokens]

group1_toks_sort <- group1_corp_c_tokDTfreqs[order(-token.count)]; group1_toks_sort.2 <- unique(group1_toks_sort)
group2_toks_sort <- group2_corp_c_tokDTfreqs[order(-token.count)]; group2_toks_sort.2 <- unique(group2_toks_sort)
group3_toks_sort <- group3_corp_c_tokDTfreqs[order(-token.count)]; group3_toks_sort.2 <- unique(group3_toks_sort)


## BIGRAMS
group1_corp_c_biDTfreqs <- group1_corp_c_biDT[,bigram.count:=.N, by = bigrams]
group2_corp_c_biDTfreqs <- group2_corp_c_biDT[,bigram.count:=.N, by = bigrams]
group3_corp_c_biDTfreqs <- group3_corp_c_biDT[,bigram.count:=.N, by = bigrams]

group1_bi_sort <- group1_corp_c_biDTfreqs[order(-bigram.count)]; group1_bi_sort.2 <- unique(group1_bi_sort)
group2_bi_sort <- group2_corp_c_biDTfreqs[order(-bigram.count)]; group2_bi_sort.2 <- unique(group2_bi_sort)
group3_bi_sort <- group3_corp_c_biDTfreqs[order(-bigram.count)]; group3_bi_sort.2 <- unique(group3_bi_sort)


## TRIGRAMS
group1_corp_c_triDTfreqs <- group1_corp_c_triDT[,trigram.count:=.N, by = trigrams]
group2_corp_c_triDTfreqs <- group2_corp_c_triDT[,trigram.count:=.N, by = trigrams]
group3_corp_c_triDTfreqs <- group3_corp_c_triDT[,trigram.count:=.N, by = trigrams]

group1_tri_sort <- group1_corp_c_triDTfreqs[order(-trigram.count)]; group1_tri_sort.2 <- unique(group1_tri_sort)
group2_tri_sort <- group2_corp_c_triDTfreqs[order(-trigram.count)]; group2_tri_sort.2 <- unique(group2_tri_sort)
group3_tri_sort <- group3_corp_c_triDTfreqs[order(-trigram.count)]; group3_tri_sort.2 <- unique(group3_tri_sort)


## TETRAGRAMS
group1_corp_c_tetraDTfreqs <- group1_corp_c_tetraDT[,tetragram.count:=.N, by = tetragrams]
group2_corp_c_tetraDTfreqs <- group2_corp_c_tetraDT[,tetragram.count:=.N, by = tetragrams]
group3_corp_c_tetraDTfreqs <- group3_corp_c_tetraDT[,tetragram.count:=.N, by = tetragrams]

group1_tetra_sort <- group1_corp_c_tetraDTfreqs[order(-tetragram.count)]; group1_tetra_sort.2 <- unique(group1_tetra_sort)
group2_tetra_sort <- group2_corp_c_tetraDTfreqs[order(-tetragram.count)]; group2_tetra_sort.2 <- unique(group2_tetra_sort)
group3_tetra_sort <- group3_corp_c_tetraDTfreqs[order(-tetragram.count)]; group3_tetra_sort.2 <- unique(group3_tetra_sort)


## PENTAGRAMS
group1_corp_c_pentDTfreqs <- group1_corp_c_pentDT[,pentagram.count:=.N, by = pentagrams]
group2_corp_c_pentDTfreqs <- group2_corp_c_pentDT[,pentagram.count:=.N, by = pentagrams]
group3_corp_c_pentDTfreqs <- group3_corp_c_pentDT[,pentagram.count:=.N, by = pentagrams]

group1_pent_sort <- group1_corp_c_pentDTfreqs[order(-pentagram.count)]; group1_pent_sort.2 <- unique(group1_pent_sort)
group2_pent_sort <- group2_corp_c_pentDTfreqs[order(-pentagram.count)]; group2_pent_sort.2 <- unique(group2_pent_sort)
group3_pent_sort <- group3_corp_c_pentDTfreqs[order(-pentagram.count)]; group3_pent_sort.2 <- unique(group3_pent_sort)

```

## Initial Exploratory Data Analysis
For this initial exploration, we will build barplots of 20 most frequent n-grams for the 3 groups. 

```{r subset data for barplots, echo=FALSE}

# Subset 20 most frequent n-grams
group1_toks_sub <- as.data.frame(head(group1_toks_sort.2, n = 20))
group2_toks_sub <- as.data.frame(head(group2_toks_sort.2, n = 20))
group3_toks_sub <- as.data.frame(head(group3_toks_sort.2, n = 20))

group1_bi_sub <- as.data.frame(head(group1_bi_sort.2, n = 20))
group2_bi_sub <- as.data.frame(head(group2_bi_sort.2, n = 20))
group3_bi_sub <- as.data.frame(head(group3_bi_sort.2, n = 20))

group1_tri_sub <- as.data.frame(head(group1_tri_sort.2, n = 20))
group2_tri_sub <- as.data.frame(head(group2_tri_sort.2, n = 20))
group3_tri_sub <- as.data.frame(head(group3_tri_sort.2, n = 20))

group1_tetra_sub <- as.data.frame(head(group1_tetra_sort.2, n = 20))
group2_tetra_sub <- as.data.frame(head(group2_tetra_sort.2, n = 20))
group3_tetra_sub <- as.data.frame(head(group3_tetra_sort.2, n = 20))

group1_pent_sub <- as.data.frame(head(group1_pent_sort.2, n = 20))
group2_pent_sub <- as.data.frame(head(group2_pent_sort.2, n = 20))
group3_pent_sub <- as.data.frame(head(group3_pent_sort.2, n = 20))

```

We now build barplots of the 20 most frequent tokens across the 3 groups.

```{r build barplots for 20 most frequent TOKENS, echo=FALSE}
# load required packages
suppressPackageStartupMessages(require("ggplot2")); suppressPackageStartupMessages(require("gridExtra"))

# Build barplots for TOKENS
group1_toks_sub$order <- factor(group1_toks_sub$tokens, as.character(group1_toks_sub$tokens))

group1_toks_sub.plot <- ggplot(group1_toks_sub, aes(x = group1_toks_sub$order, y = group1_toks_sub$token.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 1") +
    geom_bar(colour="green", fill="blue", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())


group2_toks_sub$order <- factor(group2_toks_sub$tokens, as.character(group2_toks_sub$tokens))

group2_toks_sub.plot <- ggplot(group2_toks_sub, aes(x = group2_toks_sub$order, y = group2_toks_sub$token.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 2") +
    geom_bar(colour="green", fill="blue", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())


group3_toks_sub$order <- factor(group3_toks_sub$tokens, as.character(group3_toks_sub$tokens))

group3_toks_sub.plot <- ggplot(group3_toks_sub, aes(x = group3_toks_sub$order, y = group3_toks_sub$token.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 3") +
    geom_bar(colour="green", fill="blue", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())

# Plot combined barplots for TOKENS
newplot <- grid.arrange(group1_toks_sub.plot,group2_toks_sub.plot, group3_toks_sub.plot, ncol = 3, main = "20 Most Frequent Tokens")

```

And barplots of the 20 most frequent bigrams across the 3 groups.

```{r build barplots for 20 most frequent BIGRAMS, echo=FALSE}

# Build barplots for BIGRAMS
group1_bi_sub$order <- factor(group1_bi_sub$bigrams, as.character(group1_bi_sub$bigrams))

group1_bi_sub.plot <- ggplot(group1_bi_sub, aes(x = group1_bi_sub$order, y = group1_bi_sub$bigram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 1") +
    geom_bar(colour="mintcream", fill="red2", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())


group2_bi_sub$order <- factor(group2_bi_sub$bigrams, as.character(group2_bi_sub$bigrams))

group2_bi_sub.plot <- ggplot(group2_bi_sub, aes(x = group2_bi_sub$order, y = group2_bi_sub$bigram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 2") +
    geom_bar(colour="mintcream", fill="red2", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())


group3_bi_sub$order <- factor(group3_bi_sub$bigrams, as.character(group3_bi_sub$bigrams))

group3_bi_sub.plot <- ggplot(group3_bi_sub, aes(x = group3_bi_sub$order, y = group3_bi_sub$bigram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 3") +
    geom_bar(colour="mintcream", fill="red2", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())

# Plot combined barplots for BIGRAMS
newplot <- grid.arrange(group1_bi_sub.plot,group2_bi_sub.plot, group3_bi_sub.plot, ncol = 3, main = "20 Most Frequent Bigrams")
```



```{r build barplots for 20 most frequent TRIGRAMS, echo=FALSE}

# Build barplots for TRIGRAMS
group1_tri_sub$order <- factor(group1_tri_sub$trigrams, as.character(group1_tri_sub$trigrams))

group1_tri_sub.plot <- ggplot(group1_tri_sub, aes(x = group1_tri_sub$order, y = group1_tri_sub$trigram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 1") +
    geom_bar(colour="navyblue", fill="chocolate", width=.7, stat="identity") + 
    scale_y_discrete(labels = function(x) str_wrap(x, width = 25)) +
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())


group2_tri_sub$order <- factor(group2_tri_sub$trigrams, as.character(group2_tri_sub$trigrams))

group2_tri_sub.plot <- ggplot(group2_tri_sub, aes(x = group2_tri_sub$order, y = group2_tri_sub$trigram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 2") +
    geom_bar(colour="navyblue", fill="chocolate", width=.7, stat="identity") + 
    scale_y_discrete(labels = function(x) str_wrap(x, width = 25)) +
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())


group3_tri_sub$order <- factor(group3_tri_sub$trigrams, as.character(group3_tri_sub$trigrams))

group3_tri_sub.plot <- ggplot(group3_tri_sub, aes(x = group3_tri_sub$order, y = group3_tri_sub$trigram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 3") +
    geom_bar(colour="navyblue", fill="chocolate", width=.7, stat="identity") + 
    scale_y_discrete(labels = function(x) str_wrap(x, width = 25)) +
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())

# Plot combined barplots for TRIGRAMS
newplot <- grid.arrange(group1_tri_sub.plot)
newplot2 <- grid.arrange(group2_tri_sub.plot)
newplot3 <- grid.arrange(group3_tri_sub.plot)
```


```{r build barplots for 20 most frequent TETRAGRAMS, echo=FALSE}

# Build barplots for TETRAGRAMS
group1_tetra_sub$order <- factor(group1_tetra_sub$tetragrams, as.character(group1_tetra_sub$tetragrams))

group1_tetra_sub.plot <- ggplot(group1_tetra_sub, aes(x = group1_tetra_sub$order, y = group1_tetra_sub$tetragram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 1") +
    geom_bar(colour="yellow", fill="slateblue4", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())


group2_tetra_sub$order <- factor(group2_tetra_sub$tetragrams, as.character(group2_tetra_sub$tetragrams))

group2_tetra_sub.plot <- ggplot(group2_tetra_sub, aes(x = group2_tetra_sub$order, y = group2_tetra_sub$tetragram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 2") +
    geom_bar(colour="yellow", fill="slateblue4", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())


group3_tetra_sub$order <- factor(group3_tetra_sub$tetragrams, as.character(group3_tetra_sub$tetragrams))

group3_tetra_sub.plot <- ggplot(group3_tetra_sub, aes(x = group3_tetra_sub$order, y = group3_tetra_sub$tetragram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 3") +
    geom_bar(colour="yellow", fill="slateblue4", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())

# Plot combined barplots for TETRAGRAMS
newplot <- grid.arrange(group1_tetra_sub.plot)
newplot2 <- grid.arrange(group2_tetra_sub.plot)
newplot3 <- grid.arrange(group3_tetra_sub.plot)
```


```{r build barplots for 20 most frequent PENTAGRAMS, echo=FALSE}

# Build barplots for PENTAGRAMS
group1_pent_sub$order <- factor(group1_pent_sub$pentagrams, as.character(group1_pent_sub$pentagrams))

group1_pent_sub.plot <- ggplot(group1_pent_sub, aes(x = group1_pent_sub$order, y = group1_pent_sub$pentagram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 1") +
    geom_bar(colour="lawngreen", fill="violet", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())


group2_pent_sub$order <- factor(group2_pent_sub$pentagrams, as.character(group2_pent_sub$pentagrams))

group2_pent_sub.plot <- ggplot(group2_pent_sub, aes(x = group2_pent_sub$order, y = group2_pent_sub$pentagram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 2") +
    geom_bar(colour="lawngreen", fill="violet", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())


group3_pent_sub$order <- factor(group3_pent_sub$pentagrams, as.character(group3_pent_sub$pentagrams))

group3_pent_sub.plot <- ggplot(group3_pent_sub, aes(x = group3_pent_sub$order, y = group3_pent_sub$pentagram.count))+
    geom_bar(stat="identity") + coord_flip() + xlab("") + ylab("") + ggtitle("Group 3") +
    geom_bar(colour="lawngreen", fill="violet", width=.7, stat="identity") + 
    theme(plot.background = element_blank() ,panel.grid.major = element_blank() ,panel.grid.minor = element_blank(),     
    panel.border = element_blank())

# Plot combined barplots for PENTAGRAMS
newplot <- grid.arrange(group1_pent_sub.plot)
newplot2 <- grid.arrange(group2_pent_sub.plot)
newplot3 <- grid.arrange(group3_pent_sub.plot)
```
